Land-use legacies and climate change as a double challenge to oak forest resilience: mismatches of geographical and ecological rear edges

### 2020-06-07 man/ecosystems/ms_ecosystems.Rmd
fix highlights

### Manuscript highlights
* *Quercus pyrenaica* rear-edge forests showed high resilience at tree and stand levels
* Resilience and growth response to climate followed a water-stress gradient
* Trees and stand expressed high sensitivity to drought and land-use legacies

>>>>

### Manuscript highlights
* *Quercus pyrenaica* rear-edge forests showed high resilience to drought
* Resilience and the growth response to climate followed a water-stress gradient
* Tree growth and vegetation indices were highly sensitive to drought and land-use
